An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-24 poly-embed-journal/poly-embed-journal.tex
Fixing indentation
meeting edits

\begin{definition}
  \label{def:calibrated}
  Let original loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
for all $p \in \simplex$,
  \begin{equation}
    \label{eq:calibrated}
  \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
  \end{equation}
  If $(L, \psi)$ is calibrated with respect to $\ell$, we call $\psi$ a \emph{calibrated link.}
\end{definition}
It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, in the following sense (cf.~\citep{agarwal2015consistent}).
Given feature space $\X$, fix a distribution $D \in \Delta(\X\times\Y)$.
Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
Then $(L,\psi)$ is consistent if a sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, then the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency from a generalization of~\citet{tewari2007consistency} given by~\citet{ramaswamy2016convex}.

@@

\begin{proposition}\label{prop:embed-iff-trims-equal}
  Let $L:\reals^d\to\reals^\Y_+$ have a finite representative set, and let $\ell:\R\to\reals^\Y_+$ be a discrete loss.
  Then $L$ embeds $\ell$ if and only if $\trimcover(L) = \trimcover(\ell)$.
  Furthermore, $L$ tightly embeds $\ell$ if and only if $\ell$ is injective and $\trimcover(L) = \ell(\R)$.
\end{proposition}
\begin{proof}
  \raft{This is sort of a ``clever'' proof, probably not in a good way.  Something that used Lemma X more directly would probably be better than using Bayes risk matching.  But if correct I think it's not bad.}
  As $L$ has a finite representative set, it is minimizable.
  Proposition~\ref{prop:embed-bayes-risks} gives $L$ embeds $\ell$ if and only if $\risk L = \risk \ell$.
  If $\risk L = \risk \ell$, Lemma~\ref{lem:X}(\ref{item:X-min-V}) gives $\trim(L) = \trim(\ell)$.
  For the converse, suppose $\trim(L) = \trim(\ell) =: \V$.
  Define the discrete loss $\ell_\trim : \V \to \V, v\mapsto v$.
  Then $\ell_\trim$ is injective and $\ell_\trim(\V) = \V$, so from Lemma~\ref{lem:X}(\ref{item:X-tight-embed}), both $L$ and $\ell$ tightly embed $\ell_\trim$.
  We conclude $\risk L = \risk{\ell_\trim} = \risk \ell$ from Proposition~\ref{prop:embed-iff-trims-equal}.
  The second statement also follows directly from Lemma~\ref{lem:X}(\ref{item:X-tight-embed}).
\end{proof}

@@

\begin{proof}
  Let $L$ be a fixed loss eliciting $\Gamma$, so that in particular $\risk L$ is fixed.
  Observe $L$ is minimizable by definition of elicits.
  In each case, we will show that $\risk L$ is polyhedral, and thus Lemma~\ref{lem:X} will give us the set $\Theta$ of full-dimensional level sets of $\Gamma$, uniquely determined by $\risk L$.
  In each case we will show that the relevant set of level sets is equal to $\Theta$, giving the result.

@@

@@

\begin{definition}[Polyhedron - halfspace representation\jessie{Ziegler page 28}]
	A \emph{polyhedron} $P$ is an intersection of a finite set of closed halfspaces $\H = \{H^+_{(w_i,b_i)}\}_{i=1}^k$ presented in the form $P = \cap \H$.
%	\begin{equation*}
%	P = P(A,z) = \{x \in \reals^d \mid Ax \leq z\} \qquad \textrm{ for some } A \in \reals^{m \times d}, z \in \reals^m~.~
%	\end{equation*}
\end{definition}

@@

\begin{definition}[Face, facet]
	Let $P \subseteq \reals^d$ be a convex polytope.
	A halfspace $H^+_{(w,b)}$ is \emph{valid} for $P$ if $P \subseteq H^+_{(w,b)}$.
	%A linear inequality $\inprod{w}{x} \geq b$ is \emph{valid} for $P$ if it is satisfied for all $x \in P$.
	A \emph{face} $F_{(w,b)}$ of the polytope $P$ is any set of the form
	\begin{equation*}
	F_{(w,b)} = P \cap H_{(w,b)}~,~
	\end{equation*}
	for any valid halfspace $H^+_{(w,b)}$.
	The dimension of a face $F$ is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.
	A face $F$ with $\dim(F) = \dim(P) - 1$ is called a facet.
\end{definition}

@@

\begin{definition}
	Define the function $g : \reals_+^\Y \to \reals_+$ by
	\begin{align*}
	g(x) = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~,~
	\end{align*}
	taking $g(0) = 0$.
\end{definition}
%Extend to $g(x) = \min_{v\in\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = -\infty$ otherwise.  Def $g(0) = 0$.

@@

%\item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
\item Let $\H_{\V} = \{H_v^+ \mid v\in\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\V} \cup \H_\Y$.
\end{itemize}

@@

\begin{claim}\label{claim:G-unique-facets-Hstar}
	\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
	%Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite].
	There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
	%\jessie{$\H^* \subseteq \H$ since $G = \cap \H^* = \cap \H$; something about smallest cardinality here?}
	Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet. %\raf{make formal}
\end{claim}
  \begin{proof}
  	Since $G$ is full-dimensional, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
%	We know $G$ has a halfspace representation $G = G(H', \vec 0)$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes} \jessie{Another reference: Ziegler Proposition 2.15 analagous extension}.
%	Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$. \jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
  \end{proof}

@@

\begin{claim}
	$\H_{\V^*} \subseteq \H$
\end{claim}
\begin{proof}
	$\H_{\V^*} \subseteq \H^* \subseteq \H$.
	The first subset inclusion follows by construction of $\H_{\V^*}$, and the second follows from Theorem~\ref{thm:polyhedron-uniquely-gen-facets} as $\H^*$ is the unique minimum halfspace representation of $G$, and is finite.
	\jessie{Need to be more careful?}
	%%$G = \cap \H^*$ and $\H_{\V^*} \subseteq \H$.
	%since $\H_\Y \cup \H_{\V^*}$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
\end{proof}

@@

	%subset of facet
	Moreover, the faces of $G$ are all convex polyhedra.
	Any face of $G$ is must then be a lower-dimensional face of a facet, and therefore a subset.
	\jessie{Gr\"unbaum Page 35, Section 3.1 statement 7}
\end{proof}

@@

%\begin{claim}
%	\jessie{This should probably move down to translating for properties since representative sets are at the core, about properties}
%	$\R'$ is a representative set for $L$ if and only if $\V^* \subseteq L(\R')$.
%\end{claim}
%\begin{proof}
%	Fix $v^* \in \V^*$.
%	If $\R'$ is representative, then for any $p \in \simplex$ such that , 
%	As $g$ is $1$-homogeneous and minimizable, for every $v^* \in \V^*$, there must be some $p \in \simplex$ such that $\inprod{v^*}{p} = \inf_v \inprod{v}{x}$.
%	Thus, it suffices to show subset inclusion for any $p \in \simplex$.
%	Moreover, since $\R'$ is representative, there is some $r' \in \R'$ such that $\inprod{L(r')}{p} = \inf_{v} \inprod{v}{x}$.
%	
%	For the reverse implication, $\V^*$ is representative (since $\cup_{v^* \in \V^*} F_{v^*} = \reals_+^\Y$ in Corollary 8\jessie{make reference}), so any set containing $\V^*$ is also representative.
%\end{proof}

%\begin{corollary}
%	$\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(2)}
%\end{corollary}

>>>>

\begin{definition}
  \label{def:calibrated}
  Let discrete loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
for all $p \in \simplex$,
  \begin{equation}
    \label{eq:calibrated}
  \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
  \end{equation}
  If $(L, \psi)$ is calibrated with respect to $\ell$, we call $\psi$ a \emph{calibrated link.}
\end{definition}
It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, in the following sense (cf.~\citep{agarwal2015consistent}).
Given feature space $\X$, fix a distribution $D \in \Delta(\X\times\Y)$.
Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
Then $(L,\psi)$ is consistent if a sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, then the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency from a generalization of~\citet{tewari2007consistency} given by~\citet{ramaswamy2016convex}.

@@

\begin{proposition}\label{prop:embed-iff-trims-equal}
  Let $L:\reals^d\to\reals^\Y_+$ have a finite representative set, and let $\ell:\R\to\reals^\Y_+$ be a discrete loss.
  Then $L$ embeds $\ell$ if and only if $\trimcover(L) = \trimcover(\ell)$.
  Furthermore, $L$ tightly embeds $\ell$ if and only if $\ell$ is injective and $\trimcover(L) = \ell(\R)$.
\end{proposition}
\begin{proof}
  \raft{This is sort of a ``clever'' proof, probably not in a good way.  Something that used Lemma X more directly would probably be better than using Bayes risk matching.  But if correct I think it's not bad.}
  As $L$ has a finite representative set, it is minimizable.
  Proposition~\ref{prop:embed-bayes-risks} gives $L$ embeds $\ell$ if and only if $\risk L = \risk \ell$.
  If $\risk L = \risk \ell$, Lemma~\ref{lem:X}(\ref{item:X-min-V}) gives $\trim(L) = \trim(\ell)$.
  For the converse, suppose $\trim(L) = \trim(\ell) =: \V$.
  Define the discrete loss $\ell_\trim : \V \to \V, v\mapsto v$.
  Then $\ell_\trim$ is injective and $\ell_\trim(\V) = \V$, so from Lemma~\ref{lem:X}(\ref{item:X-tight-embed}), both $L$ and $\ell$ tightly embed $\ell_\trim$.
  We conclude $\risk L = \risk{\ell_\trim} = \risk \ell$ from Proposition~\ref{prop:embed-bayes-risks}.
  The second statement also follows directly from Lemma~\ref{lem:X}(\ref{item:X-tight-embed}).
\end{proof}

@@

\begin{proof}
  Let $L$ be a fixed loss eliciting $\Gamma$, so that in particular $\risk L$ is fixed.
  By definition of elicits, $L$ is minimizable.
  In each case, we will show that $\risk L$ is polyhedral, and thus Lemma~\ref{lem:X} will give us the set $\Theta$ of full-dimensional level sets of $\Gamma$, uniquely determined by $\risk L$.
  We will prove $1 \Rightarrow 2 \Rightarrow 3 \Rightarrow 4 \Rightarrow 1$, and in each case show that the relevant set of level sets is equal to $\Theta$, giving the result.

@@

\begin{theorem}\label{thm:ie-iff-embeds-refinement}
  Let $L$ be a polyhedral loss.
  Then $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $L$ embeds a discrete loss $\ell$ and $\prop \ell$ refines $\gamma$.
\end{theorem}

@@

\begin{definition}[Polyhedron - halfspace representation\jessie{Ziegler page 28}]
	A \emph{polyhedron} $P$ is an intersection of a finite set of closed halfspaces $\H = \{H^+_{(w_i,b_i)}\}_{i=1}^k$ presented in the form $P = \cap \H$.
\end{definition}

@@

\begin{definition}[Face, facet]
  Let $P \subseteq \reals^d$ be a convex polytope.
  A halfspace $H^+_{(w,b)}$ is \emph{valid} for $P$ if $P \subseteq H^+_{(w,b)}$.
  % A linear inequality $\inprod{w}{x} \geq b$ is \emph{valid} for $P$ if it is satisfied for all $x \in P$.
  A \emph{face} $F_{(w,b)}$ of the polytope $P$ is any set of the form
  \begin{equation*}
    F_{(w,b)} = P \cap H_{(w,b)}~,~
  \end{equation*}
  for any valid halfspace $H^+_{(w,b)}$.
  The dimension of a face $F$ is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.
  A face $F$ with $\dim(F) = \dim(P) - 1$ is called a facet.
\end{definition}

@@

\begin{definition}
  Define the function $g : \reals_+^\Y \to \reals_+$ by
  \begin{align*}
    g(x) = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~,~
  \end{align*}
  taking $g(0) = 0$.
\end{definition}
% Extend to $g(x) = \min_{v\in\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = -\infty$ otherwise.  Def $g(0) = 0$.

@@

  % \item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
\item Let $\H_{\V} = \{H_v^+ \mid v\in\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\V} \cup \H_\Y$.
\end{itemize}

@@

\begin{claim}\label{claim:G-unique-facets-Hstar}
  \raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
  % Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite].
  There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
  % \jessie{$\H^* \subseteq \H$ since $G = \cap \H^* = \cap \H$; something about smallest cardinality here?}
  Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet. %\raf{make formal}
\end{claim}
\begin{proof}
  Since $G$ is full-dimensional, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
  %	We know $G$ has a halfspace representation $G = G(H', \vec 0)$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes} \jessie{Another reference: Ziegler Proposition 2.15 analagous extension}.
  %	Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$. \jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
\end{proof}

@@

\begin{claim}
  $\H_{\V^*} \subseteq \H$
\end{claim}
\begin{proof}
  $\H_{\V^*} \subseteq \H^* \subseteq \H$.
  The first subset inclusion follows by construction of $\H_{\V^*}$, and the second follows from Theorem~\ref{thm:polyhedron-uniquely-gen-facets} as $\H^*$ is the unique minimum halfspace representation of $G$, and is finite.
  \jessie{Need to be more careful?}
  %% $G = \cap \H^*$ and $\H_{\V^*} \subseteq \H$.
  % since $\H_\Y \cup \H_{\V^*}$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
\end{proof}

@@

  % subset of facet
  Moreover, the faces of $G$ are all convex polyhedra.
  Any face of $G$ is must then be a lower-dimensional face of a facet, and therefore a subset.
  \jessie{Gr\"unbaum Page 35, Section 3.1 statement 7}
\end{proof}

@@

% \begin{claim}
%   \jessie{This should probably move down to translating for properties since representative sets are at the core, about properties}
%   $\R'$ is a representative set for $L$ if and only if $\V^* \subseteq L(\R')$.
% \end{claim}
% \begin{proof}
%   Fix $v^* \in \V^*$.
%   If $\R'$ is representative, then for any $p \in \simplex$ such that , 
%   As $g$ is $1$-homogeneous and minimizable, for every $v^* \in \V^*$, there must be some $p \in \simplex$ such that $\inprod{v^*}{p} = \inf_v \inprod{v}{x}$.
%   Thus, it suffices to show subset inclusion for any $p \in \simplex$.
%   Moreover, since $\R'$ is representative, there is some $r' \in \R'$ such that $\inprod{L(r')}{p} = \inf_{v} \inprod{v}{x}$.
%   
%   For the reverse implication, $\V^*$ is representative (since $\cup_{v^* \in \V^*} F_{v^*} = \reals_+^\Y$ in Corollary 8\jessie{make reference}), so any set containing $\V^*$ is also representative.
% \end{proof}

% \begin{corollary}
%   $\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(2)}
% \end{corollary}
